\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr} % Required for the footer

% Page Margins
\geometry{a4paper, total={170mm,257mm}, left=25mm, top=25mm, right=25mm, bottom=25mm}

% Title Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}
\titleformat{\subsection}{\bfseries}{}{0em}{}

% --- FOOTER CONFIGURATION ---
% Define a custom style called 'lastpage'
\fancypagestyle{lastpage}{
    \fancyhf{} % Clear all headers and footers
    \renewcommand{\headrulewidth}{0pt} % Remove header line
    \fancyfoot[C]{\footnotesize \textit{DISCLAIMER: This document is a work of satire intended for comedic purposes only. The author accepts no liability for arguments caused by this paper. No actual algorithms were harmed in the making of this report.}}
}

% Set default style to 'plain' (just page numbers, no footer) for the rest of the doc
\pagestyle{plain} 

% Meta Data
\title{\textbf{\Large SYSTEM ARCHITECTURE MISMATCH: AN ANALYSIS OF NON-LINEAR SOCIAL ALGORITHMS IN FEMALE NEURAL NETWORK SYSTEMS}}
\author{\textbf{Seyam Bin H Rahman}}
\date{February 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
\noindent This paper investigates the severe latency and compatibility issues observed when interfacing a standard Male Logic Unit (MLU) with the advanced Female Operating System (FOS). While the MLU operates on a linear, Boolean logic structure (True/False), the FOS utilizes a complex, distributed ledger system with emotional metadata. Through field observations, this study documents critical system failures, including the ``False Positive'' Confirmation and the ``Circular Dependency'' Deadlock. The author concludes that debugging is impossible and recommends a ``Smile and Nod'' patch for system stability.
\end{abstract}

\vspace{0.5cm}

\section{INTRODUCTION}
The fundamental divergence between male and female communication protocols has long baffled engineers. The Male Logic Unit (MLU) processes data sequentially: Input $\rightarrow$ Processing $\rightarrow$ Output. For example, the command \textit{``I am hungry''} leads directly to the execution \textit{``Eat Food.''}

In contrast, the Female Operating System (FOS) appears to run on a \textbf{Quantum Superposition} principle. A variable can be ``Yes,'' ``No,'' and ``Maybe'' simultaneously until observed by a third party. This creates a hardware mismatch where the MLU fails to decrypt the high-frequency emotional data packets sent by the FOS.

\section{CASE STUDY A: THE ``UNCOMPRESSED DATA'' OVERFLOW}
\subsection{The Scenario}
I asked a female friend a very simple Yes/No question: \textit{``Did you buy the Rapid Pass?''}
All I wanted was a single bit of information: A 0 (No) or a 1 (Yes).

\subsection{The Analysis}
Instead of giving me the bit, she downloaded a 4GB file of uncompressed drama. She started telling me about the architecture of the bank, how rude the guard was, the temperature of the AC in the waiting room, and how long the line was.
I tried to stop her. I said, ``Sister, please. Just tell me. Yes or No?''
She looked at me like I had just deleted her operating system.
To me, the fact that the server was down is just a technical error. To her, it was a three-act play about the struggle of the proletariat against the banking system.

\section{CASE STUDY B: THE ``FALSE POSITIVE'' CONFIRMATION}
\subsection{The Scenario}
I asked a female colleague if she could handle a client meeting alone. I asked her specifically: \textit{``Can you handle this?''}
She said, \textit{``Yes.''}
So, logically, I prepared to leave. As I was walking out the door, she suddenly said: \textit{``Wait. You are seriously not coming?''}

\subsection{The Analysis}
This was a classic trap. When she said ``Yes,'' she didn't actually mean ``Yes.'' She meant, ``I am a strong, independent professional who can handle this, but I need you to stand there and watch me be strong and independent.''
My brain took the word ``Yes'' literally. I didn't realize that the word was encrypted with hidden emotional layers that required a password I didn't have.

\section{CASE STUDY C: THE ``MAN-IN-THE-MIDDLE'' ROUTING}
\subsection{The Scenario}
I missed a friend's wedding because I was sick. When I saw her later, I asked, \textit{``How are you?''}
She didn't answer me. Instead, she turned to her friend—who was standing right next to us—and said: \textit{``Tell him not to talk to me.''}

\subsection{The Analysis}
This was fascinating. She was standing two feet away from me. I was standing two feet away from her. But instead of a direct connection, she routed the message through a third party.
Why? Because talking to me directly would solve the problem too quickly. By using a middleman, she created ``Lag.'' She wanted me to ask, ``Why? What happened?'' repeatedly. She wasn't blocking me; she was just trying to increase the engagement metrics of the conversation.

\section{CASE STUDY D: THE ``CIRCULAR DEPENDENCY'' DEADLOCK}
\subsection{The Scenario}
A group of female friends trying to pick a restaurant.
Friend A says: \textit{``Anything is fine.''} (This is a lie).
Friend B says: \textit{``No, you pick.''}
Friend C says: \textit{``Not spicy.''}

\subsection{The Analysis}
The system froze. The processor was running at 100\%, but no decision was being made. This is what we call a ``Circular Dependency.'' Everyone is waiting for a signal from someone else, but no one is sending the signal.
The only way to fix it was a Hard Reset. I had to step in and say, \textit{``WE ARE GOING TO BURGER KING.''}
They complained, but deep down, they were relieved that someone finally terminated the process.

\section{CONCLUSION}
The mismatch between Male Logic and Female Networking is not a bug; it is a feature.
Men are like Calculators: We press 2+2, we want 4.
Women are like Generative AI: They are predicting 14,000 future scenarios based on how you looked at them three weeks ago.

It is recommended that male units do not attempt to patch this system. The optimal strategy is to smile, nod, and accept the Terms and Conditions without reading them.

\section{REFERENCES}
\begin{enumerate}
    \item Tanenbaum, A. S., \& Wetherall, D. J. (2010). \textit{Computer Networks (5th Edition).} Pearson. (Referenced for TCP/IP Routing Protocols).
    \item Tannen, D. (1990). \textit{You Just Don't Understand: Women and Men in Conversation.} William Morrow Paperbacks.
    \item Rahman, S. B. H., (Forthcoming, 2027). \textit{Chaotic harmony of Life} Unpublished Manuscript.
\end{enumerate}

% This command forces the 'lastpage' style (with the disclaimer) onto this specific page
\thispagestyle{lastpage}

\end{document}